---
title: "Assignment4-StochasticModels"
author: "Claijon da Silva"
date: "18/08/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(dplyr)
library(BayesLCA)

# store data in a object
hfm = read.csv('HarrisonFord.csv', header = TRUE)
colnames(hfm) <- c("SW","ESB","RJ","LC","LA","F")

# fit the model
res = rep(NA, 6)
for(i in 1:6){
  fit <- blca.em(hfm,i)
  res[i] = fit$BIC
}
index = which.max(res)

# fit winner group
fit <- blca.em(hfm,index)
```

## Introduction

This exercice will make the use of the Latent Class Analysis to investigate group similarities and clusters.

## Data

Nine hundred and forty three students were asked whether they very highly rated six different Harrison Ford movies or not (1=Yes, 0=No).
A summary of the data is as follows:

```{r echo = FALSE}
head(hfm)
summarise_all(hfm, funs(sum))

```

  - SW    Star Wars
  - ESB   The Empire Strikes Back
  - RJ    Return of the Jedi
  - LC    Indiana Jones and the Last Crusade
  - LA    Raiders of the Last Ark
  - F     The Fugitive

### The Latent Class Analysis
Checking groups from 1 to 6 and choosing the highest BIC

```{r echo = FALSE}
res
cat("Groups:", index, "BIC:", res[index], sep=" ")
prob = round( (0.996 * 0.912 * 0.994 * 0.768 * 0.953 * 0.732 *100 ), 2 )
```

### The Latent Class Analysis For 4 Groups
Group probabilities
Group 1   Group 2   Group 3   Group 4 
0.350     0.339     0.192     0.119

Within the groups, ie group 1, the probability for very high rate:

  - Star Wars is 99.6 %
  - The Empire Strikes Back is 91.12%
  - Return of the Jedi is 94.4%
  - Indiana Jones and the Last Crusade is 76.8%
  - Raiders of the Lost Ark is 95.3%
  - The Fugitive is 73.2%
  
```{r echo = FALSE}
library(knitr)
groups = c(1,2,3,4)
tab = as.data.frame(cbind("Groups" = groups, 
                          "SW" = fit$itemprob[,1],
                          "ESB" = fit$itemprob[,2],
                          "RJ" = fit$itemprob[,3],
                          "LC" = fit$itemprob[,4],
                          "LA" = fit$itemprob[,5],
                          "F" = fit$itemprob[,6]
                          )
)
kable(round(tab,3))
```

The probability of a member of group 1 to high rate all these movies is:
0.996 * 0.912 * 0.994 * 0.768 * 0.953 * 0.732 = `r prob`%

## Graph The Result

```{r echo = FALSE}
plot(fit)
```

The plot shows similarities among groups being that the 1st group seems to like all movies while the second group appears not to like any of Harrison Ford's movies. While group 3 and 4 show different tates for different movies.

## Conclusion


