---
title: "Assignment4-StochasticModels"
author: "Claijon da Silva"
date: "18/08/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(dplyr)
library(BayesLCA)

# get data
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/Documents - Claijon’s MacBook Pro/DataAnalytics/StochasticModels/Assignment4")

# store data in a object
hfm = read.csv('HarrisonFord.csv', header = TRUE)
colnames(hfm) <- c("SW","ESB","RJ","LC","LA","F")

```

## Introduction

This exercice will make the use of the Latent Class Analysis to investigate group similarities and clusters.

## Data

Nine hundred and forty three students were asked whether they very highly rated six different Harrison Ford movies or not (1=Yes, 0=No).
A summary of the data is as follows:

```{r echo = FALSE}
head(hfm)
summarise_all(hfm, funs(sum))

```

  - SW    Star Wars
  - ESB   The Empire Strikes Back
  - RJ    Return of the Jedi
  - LC    Indiana Jones and the Last Crusade
  - LA    Raiders of the Last Ark
  - F     The Fugitive

### Fitting Mixture Models

```{r echo = FALSE}

# Load relevant package (flexmix)
library(mixtools)

a = hfm[,1]
b = hfm[,2]
c = hfm[,3]
d = hfm[,4]
e = hfm[,5]
f = hfm[,6]

dat = cbind(a,b,c,d,e,f)
colnames(dat) <- c("SW","ESB","RJ","LC","LA","F")

dat <- makemultdata(a,b,c,d,e,f,cuts = median(c(a, b, c, d, e, f)))
colnames(dat) <- c("SW","ESB","RJ","LC","LA","F")
# Fit a G component mixture model
G<-1
fit <- multmixEM(dat, k=G)

# Examine the fit
summary(fit)
```  

### The Latent Class Analysis For 2 Groups

```{r echo = FALSE}
fit <- blca.em(hfm,2)
fit
plot(fit)
```

### The Latent Class Analysis For 3 Groups

```{r echo = FALSE}
fit <- blca.em(hfm,3)
fit
plot(fit)
```

### Flexmix

```{r echo=FALSE}
library(flexmix)

```

Fitting the survival

```{r echo=FALSE}
# fit survival

```

# Cox Reggression Model

A Cox regression model has been proposed to compare the time to reoffending, and particular interest is in the effect of the education duration and its effect on survival.
Using the coxph() function, develop an appropriate model for predicting the time to reoffending.

```{r echo=FALSE}

```
