---
title: "Assignment3-StochasticModels"
author: "Claijon da Silva"
date: "8/5/2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# libraries
library(survival)
library(ggfortify) #install.packages('ggfortify')

# get data
setwd("~/Library/Mobile Documents/com~apple~CloudDocs/Documents/Documents - Claijon’s MacBook Pro/DataAnalytics/StochasticModels/Assignment3")

# store data in a object
offend = read.csv('offend.csv', header = TRUE)
attach(offend)

# variables
time <- durat
event <- fail
X = cbind(drugs, black, married, educ)


```

## Introduction

This exercice will make the use of Kaplan-Meier estimate and Cox Regression to perform a Survival analysis on a data set of 1445 criminals.
R Programming language was used to assist in the analysis.

## Data

The frist few rows show the structure of the table.

```{r echo = FALSE}
head( offend )
```

  - durat     Time observed for
  - fail      1=Reoffended; 0=Censored
  - drugs     1=Yes; 0=No
  - black     1=Yes; 0=No
  - married   1=Yes; 0=No
  - educ      Years of schooling
  
### Time To Reoffend
Showing that meddian 71 and mean 55.37 are the average times for reoffending.
```{r echo = FALSE}
summary(time)
```

## Kaplan-Meier Estimate of time to reoffending for this population

```{r echo=FALSE}
head(Surv( time=durat, event=fail ))
```

Fitting the survival

```{r echo=FALSE}
# fit survival
fit <- survfit(Surv(durat, fail) ~ 1, data = offend)
autoplot(fit)
```

# Cox Reggression Model

A Cox regression model has been proposed to compare the time to reoffending, and particular interest is in the effect of the education duration and its effect on survival.
Using the coxph() function, develop an appropriate model for predicting the time to reoffending.

```{r echo=FALSE}
#fit=coxph(formula = Surv( durat, fail) ~ black, data = offend)
fit <- coxph(Surv(durat,fail)~educ*black, data=offend)
summary(fit)
```
